Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex
Update table with z3-trau data

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21205  & 19763 & 16528 &  3030 & 19149 \\ 
							& UNSAT    &   3963  &  3834 &  3831 &  3836 & 3828 \\
							& $\times$ &    253  &  1824 &  5062 & 18555 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    135  &   205 &    12 &    37 & 132 \\
							& UNSAT    &    343  &   221 &   100 &   111 & 82 \\
							& $\times$ &    122  &   174 &   488 &   452 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    842  &   859 &   881 &   670 & 778 \\
							& UNSAT    &   1824  &  1785 &  1785 &  1780 & 1827 \\
							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    528  &   671 &   264 &   491 & 688 \\
							& UNSAT    &    320  &   240 &   186 &   192 & 339 \\
							& $\times$ &    217  &   154 &   615 &   382 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 13 & 11 &   12 &     8 & 247 \\
							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
							& $\times$ &      2  &     6 &    15 &    55 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 & 596 \\
							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      &  22736  & 21517 & 17702 &  4253 & 21305  \\
							& UNSAT    &   8301  &  7834 &  7731 &  7649 & 7172  \\
							& $\times$ &    595  &  2281 &  6199 & 19730 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\hide{
% wider table for 30s timeout data
\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|| r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
								& UNSAT    &   2056  &   660 &   724  &   644 \\
								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
								& UNSAT    &      0  &     0 &     0  &     0 \\
								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}			& SAT      &   2857  &  1957 &  2705  &   422 \\ 
								& UNSAT    &  18567  & 16336 & 16829  & 16018 \\
								& $\times$ &    169  &  3300 &  2059  &  5153 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}
}

% latest backup of table 2
\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
								& UNSAT    &   2056  &   660 &   724  &   644 \\
								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
								& UNSAT    &      0  &     0 &     0  &     0 \\
								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}			& SAT      &   2857  &  1957 &  2705  &   422 \\ 
								& UNSAT    &  18567  & 16336 & 16829  & 16018 \\
								& $\times$ &    169  &  3300 &  2059  &  5153 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

@@

From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. The total number of failed cases is only a half to Z3, which is ranked the 2nd. In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number. We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.  If we exclude results on this function, then {\tool} has only $185$ failed cases in total. This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total. \todo{Check and revise the numbers after table updated.}

>>>>

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 & 19149 \\ 
							& UNSAT    &   3883  &  3834 &  3831 &  3836 & 3828 \\
							& $\times$ &    128  &  1824 &  5062 & 18555 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 & 132 \\
							& UNSAT    &    288  &   221 &   100 &   111 & 82 \\
							& $\times$ &    181  &   174 &   488 &   452 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &    880  &   859 &   881 &   670 & 778 \\
							& UNSAT    &   1786  &  1785 &  1785 &  1780 & 1827 \\
							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 & 688 \\
							& UNSAT    &    319  &   240 &   186 &   192 & 339 \\
							& $\times$ &    248  &   154 &   615 &   382 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 & 247 \\
							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
							& $\times$ &      4  &     6 &    15 &    55 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
							& UNSAT    &   1031  &   936 &  1021 &   958 & 596 \\
							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 & 21305  \\
							& UNSAT    &   8127  &  7834 &  7731 &  7649 & 7172  \\
							& $\times$ &    562  &  2281 &  6199 & 19730 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\hide{
% wider table for 30s timeout data
\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|| r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
								& UNSAT    &    720  &   660 &   724  &   644 \\
								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
								& UNSAT    &      0  &     0 &     0  &     0 \\
								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}
}

% latest backup of table 2
\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
								& UNSAT    &    720  &   660 &   724  &   644 \\
								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
								& UNSAT    &      0  &     0 &     0  &     0 \\
								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

@@

From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. The total number of failed cases is only a half to Z3, which is ranked the 2nd. In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number. We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.  If we exclude results on this function, then {\tool} has only $218$ failed cases in total. This is significantly better than the 2nd place tool Z3, which fails $942$ cases in total.
